Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls

### 2024-11-05 paper/paper.qmd
test

By measuring these things, we aimed to see how each factor might influence voter support in the polls. This helped us build a model to predict how the election might turn out based on the polling data we collected.

>>>>

Polling data have been used for many years to predict which candidate will win the presidential race. The results are utilized by policymakers and corporations to refine and continue their strategies.
